Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/evaluation.tex
non-subset IVs not a problem

There were various reasons why we did not infer
specifications on every looped array computation:
\begin{itemize}
\item \textbf{Non-subset induction variables} occur when the
induction variables on the RHS are not a subset of those in the LHS. These
cases are not stencils by our definition. The degenerate case of this
is to have only constant indices on the LHS. We see lots of examples
of this in loops as accumulators \eg{} computing the sum over an array;

\item \textbf{Derived induction variables} where an
index (\mintinline{fortran}{x}) is derived from an
induction variable (\mintinline{fortran}{i}) as in
\mintinline{fortran}{x = len - i};

>>>>

There were various reasons why we did not infer
specifications on every looped array computation:
\begin{itemize}
\item \textbf{Derived induction variables} where an
index (\mintinline{fortran}{x}) is derived from an
induction variable (\mintinline{fortran}{i}) as in
\mintinline{fortran}{x = len - i};
